---
title: "Sequence analysis of Persuasion Data"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

This is built upon Erika's work. Using the TraMineR package for sequence analysis. The first part is analysis of persuader's sequences.

```{r}
#install.packages("TraMineR")
library(TraMineR)
library(magrittr)
#install.packages("dplyr")
library(dplyr)
```

Load the data. And plot the frequencies of different states at each step, comparing the donated and not donated groups.

```{r, fig.width = 9, fig.asp = .5}
persuader <- read.csv("persuaderOnly.csv", stringsAsFactors = F)
persuader.alphab <- c("emo", "log", "cre", "pro","task", "other")
persuader.seq <- seqdef(persuader, 3:12, alphabet = persuader.alphab)
donate.seq <- seqdef(persuader %>% filter(persuader$donate_p==1), 3:12, alphabet = persuader.alphab)
notdonate.seq <- seqdef(persuader %>% filter(persuader$donate_p==0), 3:12, alphabet = persuader.alphab)
#seqdplot(persuader.seq, group = persuader$donate_p, border = NA)
```

Now, we need to analyse the subsequences of these groups.
```{r}
#transition <- seqetm(persuader.seq, method = "transition")
#transition
pder.seqe <- seqecreate(persuader.seq)
pder.seqestate <- seqecreate(persuader.seq, tevent = "state")
pder.seqeperiod <- seqecreate(persuader.seq, tevent = "period")
#pder.seqe[1]
#pder.seqestate[1]
#pder.seqeperiod[1]

don.seqe <- seqecreate(donate.seq)
don.seqestate <- seqecreate(donate.seq, tevent = "state")
don.seqeperiod <- seqecreate(donate.seq, tevent = "period")

ndon.seqe <- seqecreate(notdonate.seq)
ndon.seqestate <- seqecreate(notdonate.seq, tevent = "state")
ndon.seqeperiod <- seqecreate(notdonate.seq, tevent = "period")
```


There is also another function to compare subsequence frenquencies from two groups. However, there are two methods to calculate, and I don't know what they are exactly. But the Chi-square test is less strict than the other one Bonferroni test.

```{r, fig.width=5}
pdersubseq <- seqefsub(pder.seqestate, min.support = 10, constraint = seqeconstraint(count.method = 1, max.gap = 1))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort011 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.05)
discrcohort011
```

```{r, fig.width=8}
plot(discrcohort011, resid.levels = c(0.05,0.01))
```

```{r, fig.width=8, fig.height=8}
#plot(discrcohort011, resid.levels = c(0.05,0.01), rows = 1, cols = 1, ptype = "resid")
```

```{r, fig.width=10}
pdersubseq <- seqefsub(pder.seqestate, min.support = 10, constraint = seqeconstraint(count.method = 1, max.gap = 3))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort01_1 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.05)
discrcohort01_1
```

```{r, fig.width=8}
plot(discrcohort01_1, resid.levels = c(0.05,0.01))
```

```{r, fig.width=8, fig.height=8}
#plot(discrcohort01_1, resid.levels = c(0.05,0.01), rows = 1, cols = 1, ptype = "resid")
```


```{r, fig.width=8}
pdersubseq <- seqefsub(pder.seqe, min.support = 10, constraint = seqeconstraint(count.method = 1, max.gap = 1))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort111 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.05)
discrcohort111
```
```{r, fig.width=8}
plot(discrcohort111, resid.levels = c(0.05,0.01))
```

```{r, fig.width=8, fig.height=8}
#plot(discrcohort111, resid.levels = c(0.05,0.01), rows = 1, cols = 1, ptype = "resid")
```

```{r, fig.width=10}
pdersubseq <- seqefsub(pder.seqe, min.support = 10, constraint = seqeconstraint(count.method = 1, max.gap = 3))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort11_1 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.05)
discrcohort11_1
```

```{r, fig.width=8, fig.height=6}
plot(discrcohort11_1, resid.levels = c(0.05,0.01))
```

```{r, fig.width=8, fig.height=10}
#plot(discrcohort11_1, resid.levels = c(0.05,0.01), rows = 1, cols = 1, ptype = "resid")
```


```{r, fig.width = 9, fig.asp = .5}
persuader <- read.csv("persuaderPersuadee.csv", stringsAsFactors = F)
persuader.alphab  <- c("opening","askp","providep","positive","offtask","asktask","agree","disagree","cre","emo","log","other","pro","task") # the order of strategies
#persuader.alphab <- c("A1","A11","A12","A16","A17","A18","A19", "A3", "A5","A6","cre","emo","log","other","pro","task") # the order of strategies
persuader.seq <- seqdef(persuader, 3:22, alphabet = persuader.alphab)
donate.seq <- seqdef(persuader %>% filter(persuader$donate_p==1), 3:22, alphabet = persuader.alphab)
notdonate.seq <- seqdef(persuader %>% filter(persuader$donate_p==0), 3:22, alphabet = persuader.alphab)
#seqdplot(persuader.seq, group = persuader$donate_p, border = NA)
```


```{r}
#transition <- seqetm(persuader.seq, method = "transition")
#transition
pder.seqe <- seqecreate(persuader.seq)
pder.seqestate <- seqecreate(persuader.seq, tevent = "state")
pder.seqeperiod <- seqecreate(persuader.seq, tevent = "period")
#pder.seqe[1]
#pder.seqestate[1]
#pder.seqeperiod[1]

don.seqe <- seqecreate(donate.seq)
don.seqestate <- seqecreate(donate.seq, tevent = "state")
don.seqeperiod <- seqecreate(donate.seq, tevent = "period")

ndon.seqe <- seqecreate(notdonate.seq)
ndon.seqestate <- seqecreate(notdonate.seq, tevent = "state")
ndon.seqeperiod <- seqecreate(notdonate.seq, tevent = "period")
```

```{r, fig.width=10}
pdersubseq <- seqefsub(pder.seqestate, min.support = 10, constraint = seqeconstraint(count.method = 1, max.gap = 1))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort011 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.05)
discrcohort011
```
```{r, fig.width=8}
discrcohort011$subseq
#plot(discrcohort011, resid.levels = c(0.05,0.01), rows = 1, cols = 1)
```



```{r, fig.width=8}
plot(discrcohort011, resid.levels = c(0.05,0.01))
```

```{r, fig.width=8, fig.height=8}
#plot(discrcohort011, resid.levels = c(0.05,0.01), rows = 1, cols = 1, ptype = "resid")
```

```{r, fig.width=10}
pdersubseq <- seqefsub(pder.seqe, min.support = 10, constraint = seqeconstraint(count.method = 1, max.gap = 1))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort111 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.05)
discrcohort111
```

```{r, fig.width=8, fig.height=8}
plot(discrcohort111, resid.levels = c(0.05,0.01))
```


```{r, fig.width=10, fig.height=14}
#plot(discrcohort111, resid.levels = c(0.05,0.01), rows = 1, cols = 1, ptype = "resid")
```

The logic here would be:

Entropy ---> Diversity of strategies correlates with donation behaviour ---> Accumulates effect or certain single strategy effect? ---> frequency analysis show (no distinct difference of single strategy between two donation behaviours) ---> non-specific accumulation vs specific accumulation ---> markov chain model and subsequence analysis (some specific accumulations).





