---
title: "Sequence analysis of Persuasion Data"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

This is built upon Erika's work. Using the TraMineR package for sequence analysis. The first part is analysis of persuader's sequences.

```{r}
#install.packages("TraMineR")
library(TraMineR)
library(magrittr)
library(dplyr)
```

Load the data. And plot the frequencies of different states at each step, comparing the donated and not donated groups.

```{r, fig.width = 9, fig.asp = .5}
persuader <- read.csv("persuaderOnly.csv", stringsAsFactors = F)
persuader.alphab <- c("emo", "log", "cre", "pro","task", "other")
persuader.seq <- seqdef(persuader, 3:12, alphabet = persuader.alphab)
donate.seq <- seqdef(persuader %>% filter(persuader$donate_p==1), 3:12, alphabet = persuader.alphab)
notdonate.seq <- seqdef(persuader %>% filter(persuader$donate_p==0), 3:12, alphabet = persuader.alphab)
#seqdplot(persuader.seq, group = persuader$donate_p, border = NA)
```

Now, we need to analyse the subsequences of these groups.
```{r}
#transition <- seqetm(persuader.seq, method = "transition")
#transition
pder.seqe <- seqecreate(persuader.seq)
pder.seqestate <- seqecreate(persuader.seq, tevent = "state")
pder.seqeperiod <- seqecreate(persuader.seq, tevent = "period")
#pder.seqe[1]
#pder.seqestate[1]
#pder.seqeperiod[1]

don.seqe <- seqecreate(donate.seq)
don.seqestate <- seqecreate(donate.seq, tevent = "state")
don.seqeperiod <- seqecreate(donate.seq, tevent = "period")

ndon.seqe <- seqecreate(notdonate.seq)
ndon.seqestate <- seqecreate(notdonate.seq, tevent = "state")
ndon.seqeperiod <- seqecreate(notdonate.seq, tevent = "period")
```

Now we have some event sequences, we try to find the frequent subsequences. There are three types of sequences, here I put two: transition subsequences and state subsequences.

The transition subsequences are:
```{r, fig.width=10}
donsub <- seqefsub(don.seqe, min.support = 40, constraint = seqeconstraint(count.method = 1))
plot(donsub)
```


```{r, fig.width=12}
donsub <- seqefsub(don.seqe, min.support = 20, constraint = seqeconstraint(max.gap = 1, count.method = 1))
plot(donsub)
```


The state subsequences are:
```{r, fig.width=10}
donsubstate <- seqefsub(don.seqestate, min.support = 100, constraint = seqeconstraint(count.method = 1))
plot(donsubstate)
```

```{r, fig.width=12}
donsubstate <- seqefsub(don.seqestate, min.support = 10, constraint = seqeconstraint(max.gap = 1, count.method = 1))
plot(donsubstate)
```

There is also another function to compare subsequence frenquencies from two groups. However, there are two methods to calculate, and I don't know what they are exactly. But the Chi-square test is less strict than the other one Bonferroni test.

```{r, fig.width=10}
pdersubseq <- seqefsub(pder.seqestate, min.support = 10, constraint = seqeconstraint(count.method = 1, max.gap = 1))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort011 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.1)
#discrcohort011
plot(discrcohort011)
```


```{r, fig.width=10}
pdersubseq <- seqefsub(pder.seqestate, min.support = 10, constraint = seqeconstraint(count.method = 1))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort01_1 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.1)
#discrcohort01_1
plot(discrcohort01_1[1:30])
```

```{r, fig.width=10}
plot(discrcohort01_1[31:60])
```

```{r, fig.width=10}
plot(discrcohort01_1[61:90])
```

```{r, fig.width=10}
plot(discrcohort01_1[91:120])
```

```{r, fig.width=10}
plot(discrcohort01_1[121:133])
```

```{r, fig.width=10}
discrcohort01_1
```


```{r, fig.width=10}
pdersubseq <- seqefsub(pder.seqe, min.support = 10, constraint = seqeconstraint(count.method = 1, max.gap = 1))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort111 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.1)
#discrcohort111
plot(discrcohort111)
```




```{r, fig.width=10}
pdersubseq <- seqefsub(pder.seqe, min.support = 10, constraint = seqeconstraint(count.method = 1))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort11_1 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.1)
#discrcohort11_1
plot(discrcohort11_1[1:30])
```

```{r, fig.width=10}
plot(discrcohort11_1[31:60])
```

```{r, fig.width=10}
plot(discrcohort11_1[61:83])
```

```{r, fig.width=10}
discrcohort11_1
```


```{r, fig.width = 9, fig.asp = .5}
persuader <- read.csv("persuaderPersuadee.csv", stringsAsFactors = F)
persuader.alphab  <- c("opening","askp","providep","positive","offtask","asktask","agree","disagree","cre","emo","log","other","pro","task") # the order of strategies
#persuader.alphab <- c("A1","A11","A12","A16","A17","A18","A19", "A3", "A5","A6","cre","emo","log","other","pro","task") # the order of strategies
persuader.seq <- seqdef(persuader, 3:22, alphabet = persuader.alphab)
donate.seq <- seqdef(persuader %>% filter(persuader$donate_p==1), 3:22, alphabet = persuader.alphab)
notdonate.seq <- seqdef(persuader %>% filter(persuader$donate_p==0), 3:22, alphabet = persuader.alphab)
#seqdplot(persuader.seq, group = persuader$donate_p, border = NA)
```



```{r}
#transition <- seqetm(persuader.seq, method = "transition")
#transition
pder.seqe <- seqecreate(persuader.seq)
pder.seqestate <- seqecreate(persuader.seq, tevent = "state")
pder.seqeperiod <- seqecreate(persuader.seq, tevent = "period")
#pder.seqe[1]
#pder.seqestate[1]
#pder.seqeperiod[1]

don.seqe <- seqecreate(donate.seq)
don.seqestate <- seqecreate(donate.seq, tevent = "state")
don.seqeperiod <- seqecreate(donate.seq, tevent = "period")

ndon.seqe <- seqecreate(notdonate.seq)
ndon.seqestate <- seqecreate(notdonate.seq, tevent = "state")
ndon.seqeperiod <- seqecreate(notdonate.seq, tevent = "period")
```

```{r, fig.width=10}
donsub <- seqefsub(don.seqe, min.support = 120, constraint = seqeconstraint(count.method = 1))
plot(donsub)
```


```{r, fig.width=12}
donsub <- seqefsub(don.seqe, min.support = 50, constraint = seqeconstraint(max.gap = 1, count.method = 1))
plot(donsub)
```

```{r, fig.width=10}
donsubstate <- seqefsub(don.seqestate, min.support = 200, constraint = seqeconstraint(count.method = 1))
plot(donsubstate)
```


```{r, fig.width=12}
donsubstate <- seqefsub(don.seqestate, min.support = 50, constraint = seqeconstraint(max.gap = 1, count.method = 1))
plot(donsubstate)
```


```{r, fig.width=10}
pdersubseq <- seqefsub(pder.seqestate, min.support = 10, constraint = seqeconstraint(count.method = 1, max.gap = 1))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort011 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.1)
#discrcohort011
plot(discrcohort011[1:30])
```

```{r, fig.width=10}
plot(discrcohort011[31:52])
```
```{r}
discrcohort011
```



```{r, fig.width=10}
pdersubseq <- seqefsub(pder.seqe, min.support = 10, constraint = seqeconstraint(count.method = 1, max.gap = 1))
cohort <- factor(persuader$donate_p > 0, labels = c("no donation", "donation"))
discrcohort111 <- seqecmpgroup(pdersubseq, group = cohort, method = "chisq", pvalue.limit = 0.1)
#discrcohort111
plot(discrcohort111[1:30])
```


```{r, fig.width=10}
plot(discrcohort111[31:48])
```



```{r}
discrcohort111
```










